\chapter{Swampland Programs}
\label{Chapter1}
This chapter will be devoted to the introductions of the Swampland programs. In the first section, we will review some basics of the effective field theory. Then, with a certain understanding of EFTs, the following sections will introduce concepts of the Swampland and the Swampland programs. To keep things focused for the purpose of this thesis, stresses are mainly put on the Swampland Distance Conjecture. For statements and discussions about other conjectures and relations between them, we will provide useful references.
\section{Effective Field Theory}
Nature around us comes from a lot of factors. From the perspective of physics, physical phenomena occur in a variety of scales of size: from electrons, nuclei, atoms, molecules to planets, stars, galaxies, and so on. Physics has been progressing because scientists could understand them independently without the necessity of understanding all of them at once. What made it possible is a property of nature called decoupling, which claims that most of the information regarding physics at short distance scale has nothing to do with ones at a long-distance scale. For instance, suppose a glass of water which consists of numerous $H_{2} O$ molecules. Each molecule is made from atoms which involve electrons executing orbits around a nucleus. A nucleus itself consists of protons and neutrons, and there are more complicated structures as we inquire into it deeper and deeper. However, we are accustomed to being able to know the dynamics of water without knowing such complex structures. The notion of decoupling is important because in some case it is not necessary to know about the detailed properties of nuclei in order to unravel atomic physics, just as ignorance about atoms does not keep us from an understanding of laws of nature at larger scales such as fluid dynamics and motions of springs. Laws of nature are also described by quantum field theories (QFTs), which share the property of decoupling. When a particular QFT for short-distance physics is investigated, it is apparently useful if we are able to identify which observables are relevant for a description of the theory and those from which they decouple. A mathematical tool for exploiting the property of decouples is effective field theories (EFTs). Since the Swampland program involves EFT coupled to gravity, in this chapter, we will first start reviewing concepts of EFTs. A useful reference for this section might be as \parencite{burgess_introduction_2020}. 
\subsection{Basic Ideas}
As stated above, the key idea behind EFTs is that physics is simplified when viewed from a distance. For instance, suppose a system of electric charges within a region of a space of characteristic size $\sim l$. If one may want to study their effects at a distance much larger than $l$, $r \gg l$, detailed knowledge of the charge distribution is not required. Instead, one can approximate the system by a few terms in the multipole expansion, such as the total charge, the dipole moment, and so on. This is the same for particle physics. However, it is more common to use the energy scale rather than the length scale $E = l^{-1}$ to distinguish different regimes. Thus, long distances can be interpreted as low energies. In this sense, experiments with the characteristic energy of order $E$ do not require detailed knowledge of physics at higher energy scales $\Lambda \gg E$. The property of decoupling enables us to pursue particular physics by separating theoretically the system with various energy scales when entire theories (full theories) are still unknown. In addition, even if full theories or other EFTs at higher energy scales are known, EFTs are great tools to simplify their computations by lowering scales.  



\section{The Swampland Program}
In the previous section, the concepts of EFTs were reviewed. Thanks to the property of decoupling, we are able to study physics starting from low-energy regimes where we are supposed to have enough knowledge without knowing anything about high-energy scale physics. This also enables us to scrutinize physics in higher energy scales beginning from low-energy EFTs whose structures are well-understood. However, how far is this procedure valid? In other words, is there a specific energy scale above which this "bottom-up" study ceases to work? Let us think about the black hole and the Schwarzschild radius $R_{s}$. As the mass increases (i.e. the energy increases), and finally becomes Planck scale $M \sim m_{p} \sim 10^{28} \text{eV}$, the Compton wavelength is shorter than the Schwarzschild radius, and therefore the more detailed structures are hiding behind the event horizon. In this sense, the Planck scale might be where the structure of EFTs will be collapsing. In addition, in order to describe physics at the Planck scale, it is believed that the theory of quantum gravity is needed. Hence, if we take quantum gravity into account, not all low-energy (IR) EFTs that seem to be consistent are valid at the Planck scale. That is, there are supposed to be subsets of EFTs that are inconsistent in consideration of quantum gravity inside the entire set of consistent effective QFTs. This is the emergence of the idea of the Swampland and the necessity of the Swampland program. The aim is, roughly speaking, to determine conditions which distinguish such subsets. In this section, we will introduce the concept of the Swampland, and provide a few conjectures needed for the purpose of this thesis. Possible references for this section and more are for example \parencite{agmon_lectures_2022, grana_swampland_2021, vafa_string_2005}. 

\subsection{The Swampland and The Swampland Program}
From the EFTs perspective, at an energy scale much smaller than the Planck scale, we can exploit the decoupling property to study low-energy physics. Once a theory below a certain energy is well understood, we proceed to investigate a new physics whose scale is a little higher than the former one's. By repeating this process, EFTs have been thought of as approaches to unknown ultraviolet physics. Nevertheless, at the Planck scale, where it is believed that quantum gravity has to be taken into account, it is predicted that the structure of EFTs will be problematic. Normally, when phenomenological problems are considered, since the energy scale is typically much smaller than the Planck scale, the effect of gravity can be ignored or considered classically. While in the case when the energy scale is extremely high, we have to think about the quantization of gravity, it has been believed as an independent problem at a UV scale. Recent research, however, has been revealing the possibility that requirements of consistency by quantum gravity are expected to have certain restrictions on its infrared (IR) low-energy physics. This observation suggests that, on contrary to the EFTs' property of decoupling, low-energy phenomenological problems and UV quantum gravity are closely related to each other, and should not be considered independently.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=5]
        \draw[->] (0,0) -- (0,1) node[above=3pt]{Energy Scale} ;
        \shadedraw[blue] (0, 0.8) rectangle (2, 0.9);
        \draw (0, 0.1) rectangle (2, 0.3);
        \draw (1,0.85) node{Quantum Gravity};
        \draw (1, 0.95) node{Planck scale};
        \draw (1, 0.15) node{low energy (IR): Constraints from quantum gravity?};
        \draw[line width=1pt, red] (0.3,0.3) .. controls(0.3, 0.5) .. (0.4, 0.8) node[pos = 0.5, right]{somehow connected to each other};
    \end{tikzpicture}
    \caption{On the contrary to the EFTs feature of UV/IR decoupling, it is suggested that low-energy physics is not independent of extremely high-energy theories (quantum gravity).}
    \label{fig:UV/IR mixing}
\end{figure}
Below the Planck scale, $M_{p}$, theories can be described by an EFT coupled to classical gravity, since the effect of quantum gravity is ignored. Picking a theory of quantum gravity, we can find one low-energy EFT corresponding to such theory at the Planck scale. Now let us consider oppositely. That is, if we consider an EFT, can we obtain a theory of quantum gravity which is compatible with it? The answer to this question separates the entire set of EFTs coupled to gravity into two subsets. One is the set of EFTs obtained as consistent low-energy theories of quantum gravity, and the other is its complementary which cannot be valid. The former is called the landscape, and lthe atter is the Swampland.

\begin{tcolorbox}[title=The Swampland,
    title filled=false,
    colback=blue!5!white,
    colframe=blue!75!black]
    The set of consistent low-energy EFTs that seem to be consistent, but cannot be compatible in consideration of quantum gravity. 
\end{tcolorbox} 
\begin{figure}
    \centering
    \begin{tikzpicture}[scale=5]
        \draw[fill= green!20] (0,0) ellipse (1 and .5);
        \draw[fill=white] (0.4,0.1) circle (.3);
        \draw (-0.3,-.2) node{Swampland};
        \draw(.4,.1) node{Landscape};
    \end{tikzpicture}
    \caption{The entire set of EFTs coupled to gravity is separated into subsets: Landscape and Swampland. Green region is Swampland, and white circle indicates Landscape.}
    \label{fig:set}
\end{figure}
Figure \ref{fig:set} shows the entire set of EFTs coupled to gravity divided into landscape and the Swampland. The attempt to find out the boundary which divides the landscape and the Swampland, and reveal constraints from quantum gravity is the Swampland program.
 
\tdplotsetmaincoords{80}{100}

\begin{figure}[h]
\begin{tikzpicture}[scale=4,tdplot_main_coords]


\draw[thick,->] (0,0,0) -- (1,0,0) node[anchor=north east]{Theory Space};
\draw[thick,->] (0,0,0) -- (0,1,0) node[anchor=north west]{Theory Space};
\draw[thick,->] (0,0,0) -- (0,0,1) node[anchor=south]{Energy Scale};

\draw(0.5,0.5,0) circle (0.45) node[below = 9pt] {Swampland};
\shadedraw[blue](0.6,0.6,0) circle (0.1);
\draw[blue,thick](0.62,0.5,0) parabola (0.6,0.6,0.9);
\draw[blue,thick](0.6,0.705,0) parabola (0.6,0.6,0.9) node[above = 1pt] {Quantum Gravity};
\draw[->] (1.2,1.2,0) node[below] {Landscape} --  (0.61,0.68,0);
\end{tikzpicture}
\caption{EFTs on the theory space. There is a landscape inside the Swampland of EFTs. Since the constraints get more strict at the higher energy scale, the space consistent with QG forms a cone shape.}
\label{fig:swampland}
\end{figure}
Notice that constraints which define those boundaries should vanish as we decouple gravity since once we no longer consider gravity all EFTs are consistent. This implies that the higher the energy scale at which the EFT is supposed to be valid is, the more strict the constraints are. It is shown in figure \ref{fig:swampland}, where the landscape at various energy scales is depicted as the blue cone. The area of landscape becomes smaller and smalelr as the energy increases, and we get closer and closer to Planck scale where we consider quantum gravity, and ends up with a consistent theory of quantum gravity. \\

\indent As repeatedly stated, there is a specific cut-off, say, $\Lambda$ above which the EFT is no longer valid. It is necessary for the EFT to be modified so that the new EFT is valid above the cut-off $\Lambda$ with some new cut-off $\Lambda'$ by integrating in new degrees of freedom, as opposed to integrating out when obtaining an EFT given some UV theory. However, this process cannot be proceeded indefinitely: no EFT cannot deal with infinitely many degrees of freedom. Therefore, any EFT has a certain cut-off where it cannot be modified anymore to obtain a consistent theory coupled to Einstein gravity. This leads to an important notion. An EFT is determined if it is on the Swampland or the landscape not only by whether it is possible to be UV completed in QG, but also by whether it is not broken down, that is, it is valid or not up to such a new cut-off. This fact can be seen from figure \ref{fig:swampland} and is shown more clearly in figure \ref{fig:cross}. Given an EFT belonging to the landscape at some lower energy scale, it belongs to the Swampland once the energy scale is greater than specific value. 

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale = 5]

        \draw[->] (0,0) -- (1,0);
        \draw[->] (0,0) -- (0,1) node[above=3pt]{Energy};
        \shadedraw[left color=blue!80!white,right color=blue!20!white, draw=blue] (0,0) -- (0,0.8) to [out=270, in=130] (0.8,0) -- cycle
        (0,0.2) node[left=3pt]{$E_{1}$}
        (0,0.5) node[left=3pt]{$E_{2}$}
        (0.3,0.1) node{Landscape}
        (0.7,0.6) node{Swampland};
        \draw[style=dashed] (0.3,0) node[below=3pt]{EFT} -- (0.3,0.8);
        \draw[style=dashed] (0,0.35) node[left=3pt]{$E_{0}$} -- (0.9,0.35);
        \draw[style=dashed] (0,0.2) -- (0.9,0.2);
        \draw[style=dashed] (0,0.5) -- (0.9,0.5);
        \filldraw[black](0.3,0.35) circle (0.5pt);
    \end{tikzpicture}
    \caption{This shows the cross section of figure \ref{fig:swampland}. Given an EFT at some lower energy scale, it belongs to the landscape as long as its characteristic energy is below $E_{0}$. However, the same EFT turns to be in the Swampland if the energy scale is above it. For instance, this EFT is in the landscape if it provides a description of physics of energy $E_{1}$, while it is in the Swampland if it does of $E_{2}$.}
    \label{fig:cross}
\end{figure}
Thus, whether an EFT belongs to the Swampland or the landscape is depending on at which energy scale it is used for an illustration of a physical system. As such energy increases, there are more strict constraints, and eventually the landscape gets smaller and smaller.\\
\indent To achieve concrete conditions which determine the boundaries between the Swampland and the landscape, phenomenological consequences, a lot of statements have been proposed. Those are called the Swampland conjectures.

\subsection{Swampland Conjectures}
At the moment, the Swampland conjectures are still proposals, not theorems because they have not been fully proven. That is why they are named conjectures. Yet, researches in recent years have found a large amount of evidence for some of them, and expectations that those conjectures might open the doors to the novel features of quantum gravity are increasing. Figure \ref{fig:connection} shows a map of conjectures as well as connections between them.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}
        \path[mindmap,concept color=black,text=white]
    node[concept] {No Global Symmetries}
    [clockwise from=0]
    child[concept color=green!50!black] {%
      node[concept](WG){Weak Gravity Conjecture}
      [clockwise from=0]
      child {node[concept] {Non-SUSY AdS Instability Conjecture} }
      %child {node[concept] {data structures} }
      %child {node[concept] {pro\-gramming languages} }
      %child {node[concept] {software engineer\-ing} }
    }  
    child[concept color=blue] {%
      node[concept](DC) {Swampland Distance Conjecture}
      [clockwise from=-30]
      child {node[concept] {No deSitter} }
      child {node[concept] {No Scale Separation in AdS} }
    }
    child[concept color=red] {node[concept] {Completeness Hypothesis} }
    child[concept color=orange] {node[concept] (TC){Trivial Cobordism} };
    \begin{pgfonlayer}{background}
        \draw [circle connection bar]
        (WG) edge (DC);
    \end{pgfonlayer}
    \end{tikzpicture}
    \caption{A schematic map of the Swampland conjectures}
    \label{fig:connection}
\end{figure}
In the following sections, only selected conjectures will be discussed in detail, which are most relevant for the thesis. The connections between conjectures might indicate that some of them are equivalent statements with different appearances. Unifying them by better understanding of QG in the future is one of the goals of this area.

\section{No Global Symmetries in Quantum Gravity}
The absence of global symmetries is considered as the first Swampland conjecture, and widely accepted. Also, many of the Swampland conjectures can be considered as attempts to expand the idea that quantum gravity should have no global symmetries \parencite{banks_symmetries_2011}. The statement of the conjecture is as follows:
\begin{tcolorbox}[title=No Global Symmetries Conjecture,
    title filled=false,
    colback=blue!5!white,
    colframe=blue!75!black]
    There are no exact global symmetries in quantum gravity.  %\textbf{tcolorbox}.
\end{tcolorbox} 
First of all, it is worth recalling briefly that a global symmetry is defined as an invariance under transformations described by a unitary operator commuting with the Hamiltonian. According to Noether's theorem, the continuous symmetry of a system indicates the existence of the conserved quantity, or charge, in it. For instance, the spatial translational symmetry leads to the conservation of momentum. There are a few kinds of arguments which support this conjecture. One motivation is black hole physics. In order to illustrate what would make it invalid if a global symmetry is allowed in quantum gravity, assume that there \emph{is} an EFT coupled to gravity with a global symmetry. In the spectrum of an EFT there are supposed to be states charged under such global symmetry. Suppose a black hole is charged by sending a charged state into it, it will evaporate decreasing its mass but maintaining its charge because Hawking radiation contains the same number of positive/negative charged particles. Letting it evaporate completely, the charge is supposed to vanish. Thus, it leads to a violation of the charge conservation. Also, even if such evaporation stops, and ends up with a remnant of mass $M \sim M_{P}$, since, according to the No-hair theorem for black hole \parencite{agmon_lectures_2022, israel_event_1967}, stable black holes can be distinguished from outside only by its mass, angular momentum, and gauge charge, it is impossible to determine its global charge given a black hole of a specific mass. Therefore, this process would violate charge conservations in a global symmetry as we started with non-zero charge and all the charge has disappeared after the evaporation of the black hole and no net charge has come out. Hence, in order to avoid this contradiction, global symmetries must be forbidden in any theory of quantum gravity.\\
\indent Another discussion against the existence of global symmetries is motivated by stable remnants of black holes. As mentioned above, starting with a charged particle we would end up with a remnant of Planckian size. Because this can happen for black holes in any representation of the symmetry group, we would eventually have an infinite number of stable remnants \parencite{grana_swampland_2021}. Having an infinite number of states below a fixed mass scale is considered to be problematic \parencite{susskind_trouble_1995}. However, it is not that simple to prove this inconsistency since here we are in Planckian size and the semiclassical description would break down. It has been also discussed that the existence of those remnants may violate the covariant entropy bound \parencite{banks_symmetries_2011}. The entropy associated with the remnant is supposed to be finite according to this bound, which contradicts that we would have infinitely many different states that may lead to the same black hole geometry implying infinite entropy.
This discussion can be extended to discrete symmetries and also to more generic global symmetries. Those are followed by the proposal of the Cobordism conjecture \parencite{mcnamara_cobordism_2019}.  \\
\indent The arguments above are rather motivations than proofs to grasp good intuitions for the conjecture. There is more formal evidence mainly from string theory. In particular, it is stated that there is no continuous global symmetry in the target space of perturbative string theory \parencite{polchinski_string_1998-1}. Here we will briefly provide the proof for the case of bosonic string theory. For any global symmetry in the world sheet, we have a worldsheet charge given:
\begin{align}
    Q = \frac{1}{2\pi i} \oint (dzj_{z} - d\bar{z} j_{\bar{z}})
\end{align}
where $j_{z}$ and $j_{\bar{z}}$ are the symmetry currents. These char must be conformally invariant, and thus they transform as $(1,0)$, $(0,1)$ tensors respectively. Then we can build vertex operators in the forms:
\begin{align}
    j_{z}\bar{\partial} X^{\mu}e^{ikX} ,& \qq{} \partial X^{\mu} j_{\bar{z}}e^{ikX}
\end{align}
They create massless gauge vectors in the target space coupling to the left and right moving parts of the charge Q. Therefore, any global symmetry in the worldsheet turns into a gauge symmetry in the spacetime, and not into a global symmetry. So far, there is no counterexample of this conjecture. There is also a discussion through AdS/CFT and holography shown in \parencite{harlow_symmetries_2021, harlow_constraints_2019,harlow_tasi_2018}.  \\
\indent It is important to note that it is permitted that there is a low-energy theory with global symmetry, as long as at higher energies such symmetry is gauged or broken. While it still gives an understanding of the principles of quantum gravity, the No-global symmetries conjecture doesn't provide meaningful phenomenological constraints since nothing about at which scale such a global symmetry gets forbidden is stated. However, it is followed by other conjectures such as the Weak Gravity Conjectures and the Swampland Distance Conjecture, which give more concrete constraints, as expansions and refinements of the concept of the impossibility of the existence of the exact global symmetries in quantum gravity. 

\section{Completeness}
While global symmetries are forbidden, having gauge symmetries in quantum gravity is possible. However, it may be important to study any relations between global and gauge symmetries in order to see constraints on theories with gauge symmetries in quantum gravity. One connection will be discussed later, which corresponds to sending the gauge coupling $e$ of a gauge symmetry to zero. In this chapter, we will provide another relation which may motivate to introduce the Completeness Conjecture. \\
\indent Consider an Einstein-Maxwell theory with simply a U(1) gauge field with gauge coupling e given:
\begin{align}
    S = \int d^{4}X \sqrt{-g}[\frac{M_{p}^{2}}{2}R - \frac{1}{4e^{2}} F^{2}]
\end{align}
The local gauge transformation is given with a scalar parameter $f(x)$ as $A_{\mu} \rightarrow A_{\mu} + \partial _{\mu} f$. In addition, we consider another transformation $A_{\mu} \rightarrow A_{\mu} + \sigma _{\mu}$ where $\sigma$ satisfies:
\begin{align}
    \label{eq:gauge}
    \partial _{\nu} \sigma _{\mu} - \partial _{\mu} \sigma _{\nu} =0
\end{align}
Gauging the symmetry $\sigma _{\mu}$ is equivalent to dropping the condition eq.\ref{eq:gauge}. It implies that there would be an anti-symmetric tensor to transform so that we could retain gauge invariance. If we can maintain \ref{eq:gauge}, then it becomes an example of a global symmetry. In quantum gravity framework, since we are expecting that global symmetry is absent, we also believe in a certain obstacle to the existence of such a global symmetry. \\
\indent A natural idea to break the global symmetry is introducing charged matters. The gauge covariant derivative for a charged field is invariant under only $\partial _{\mu} f$. This notion thus leads to an idea that in consideration of quantum gravity, there is not supposed to be a U(1) gauge symmetry with no matter charge. This ends up with a more general statement named the Completeness Conjecture defined as follows:
\begin{tcolorbox}[title=Completeness Conjecture,
    title filled=false,
    colback=blue!5!white,
    colframe=blue!75!black]
    A gauge field theory, coupled to gravity, must have states of all possible gauge charges consistent with Dirac quantization under the gauge symmetry \parencite{polchinski_monopoles_2004}.  %\textbf{tcolorbox}.
\end{tcolorbox} 
Note that the Completeness Conjecture does not restrict what the mass of the states must be. So it is possible that they have a mass, for instance, around the Planck mass.

\section{Swampland Distance Conjecture}
We have seen previously that there cannot be global symmetries in quantum gravity and completeness as the core of the Swampland program. However, it does not give phenomenological meaning unless we can restrict how approximate a global symmetries can be accepted, and whether there is any bound on the mass of some of the charged states. If not, we have constraints only on the full theory, not on the low energy EFTs. Therefore, the Swampland program will have very little significance unless we have also statements on quantitative constraints. For this reason, there are also conjectures which deal with these questions; they try to sharpen these propositions and quantify how close we can approach the situations where the global symmetries would be restored. For instance, we can a priori recover continuously a U(1) global symmetry by sending the gauge couplimg to zero, and it is not allowed in quantum gravity according to the absence of global symmetries. Trying to study how string theory makes it forbidden, and what kinds of defects would happen if we try to do this may show significant information about the constraints that an EFT has to obey to be compatible with quantum gravity. In this chapter we will see the Swampland Distance Conjecture as one of such conjectures. \\
\indent The Swampland Distance Conjecture (SDC) is the one of the Swampland conjectures which give certain quantitative constraints. It provides a restriction on the mass scales and the field distance of an EFT of quantum gravity when it is getting closer to where a global symmetry is restored. \\
\indent The motivation for the conjecture comes from the investigation in a moduli space, which is a space parametrized by the vacuum expectation value of some scalar fields. It is in particular interested in that space to observe how an EFT changes as moving toward a certain direction where a global symmetry gradually is recovered, that is, some gauge coupling decreases to zero, because an exact global symmetry is not acceptable in quantum gravity. Therefore it is expected that there would be some phenomena in such limits in order to protect a theory from getting back a global symmetry. One natural assumption to do so is that such poins are infinitely far away in a space so that the exact global symmetries cannot be recovered. In addition, as an approximate global symmetry is getting exact as moving towards those limits, it is reasonable that an EFT is supposed to become an invalid description continuously. That is also predicted by the consequence of the Weak Gravity Conjecture. \\
\indent One important key point is that it is characteristic for a quantum gravity. Without considerring the quantum gravity, it is perfectly fine to have a point where a gauge coupling vanishes at infinite distance, and being close to it with maintaining a valid theory. Once the quantum gravity is ,however, taken into account, since having an exact global symmetry is strictly forbidden, an EFT should break down continuously as being closing to those limits. This can be generalized to other types of global symmetries. The Swampland Distance Conjecture provides information how an EFT behaves when approaching infinite distance limits in a moduli space, and what features of quantum gravity makes it happen. 
\subsection{Moduli Space}
To begin with, let us clarify the notion of moduli space. For our purpose, the notion of moduli space denotes the space of different vacua. Suppose we have scalar fields $\phi ^{i}$, $i =1,\dotso ,n$, with a background and an effective action $\Gamma$. The expectation value of the scalar fields extremizes this effective action, that is:
\begin{align}
    \fdv{\phi ^{i}} \Gamma (\expval{\phi ^{i}}) = 0
\end{align}
Once we find a quantum mechanically stable background, we can study perturbations around such a background. Assume that the effective action at low-energy regimes can be approximated with the action:
\begin{align}
    \Gamma = \int d^{d}x \lbrace \frac{1}{2} g_{ij} \partial _{\mu} \phi ^{i} \partial ^{\mu} \phi ^{j} - V_{\text{eff}} (\phi ^{i}) \rbrace
\end{align}
plus terms with fields other than scalars. Now we want to find values of scalar fields that make the potential minimum. This is not necessarily a single point, but can be a manifold. Because the potential remains constant in the direction of field space that potential stays minimum, they are called the flat directions of the field space. Let us assume the minimum value of the potential is zero. \\
\indent The subspace where $V_{\text{eff}} = 0$ of the field space is called the moduli space and it represents the space of different vacua. Assuming the moduli space is parametrized by the vacuum expectation values of scalar fields $\phi ^{I}$. The kinetic term for those scalar fields takes the form as follows:
\begin{align}
    \int d^{d}x \frac{1}{2} g_{IJ} (\phi) \partial _{\mu} \phi ^{I} \partial ^{\mu} \phi ^{J}  
\end{align}
where $g_{IJ}$ can be thought of as a metric on the field space. This action is apparently the non-linear sigma model. Using this metric, we can compute geometric quantities associated with this moduli space such as the geodesic distance and volume.

\subsection{preliminary Introduction to String Theory}
Since the Distance conjecture is closely related to the string theory, it is essential to provide a basic introduction to it. It will be based on familiar discussions covered by standard textbooks such as \parencite{polchinski_string_1998, becker_string_2006, blumenhagen_basic_2013} for the string theory. \parencite{agmon_lectures_2022} also provides similar discussions.

\subsubsection{The Nambu-Goto Action}
Consider a point particle and assume it propagates in D-dimensional spacetime $\mathbb{R}^{1,D-1}$. We can assign the coordinates as $X^{0} = t$ and $X^{i}$, with $i = 1, \dotso , D-1$ for the description of the motion of the particle. Then its motion is associated with a world-line $\gamma$ which identifies $X^{i} (X^{0})$. Also, the particle world-line in relativistic coordinates can be described by a world-line parameter $\tau$ so that $\gamma$ specifies $X^{\mu}(\tau)$, where $\mu = 0,1,\dotso , D-1$ :
\begin{align}
    \gamma : \tau \hookrightarrow X^{\mu} (\tau) \in \mathbb{R} ^{1,D-1}
\end{align}
\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=5]
        \draw[->] (0,0) -- (1,0) node[right=1pt]{$X^{i}$};
        \draw[->] (0,0) -- (0,1) node[left=2pt] {$X^{0}$};
        \draw[->, red] (.5,.2) .. controls (.8,.4) .. (.7,.5) node[right=2pt,black] {$\tau$};
        \draw[red] (.7,.5) .. controls (.5,.8) .. (.75,.9);
        \draw[->, blue!70] (.8,.8) node[right=3pt,black]{world-line, $\gamma$} -- (.65,.65);
    \end{tikzpicture}
    \caption{Illustration of the world-line of a moving particle.}
    \label{fig:worldline}
\end{figure}
Figure \ref{fig:worldline} shows the description of the particle motion. \\
\indent In Minkowski space, the line element is given:
\begin{align}
    ds^{2} = \eta_{\mu \nu} dX^{\mu} dX^{\nu} 
\end{align}
Then we can write an action for a particle, which can be simply written as the length of time-like world-line:
\begin{align}
    S_{\text{NG}} = -m\int _{\gamma} \sqrt{-ds^{2}} = -m\int _{\gamma} (-\dot{X}^{2})^{1/2} d\tau
\end{align}
where $\dot{X} ^{\mu} = \pdv{X^{\mu}}{\tau}$, $\dot{X} ^{2} = \eta _{\mu \nu} \dot{X}^{\mu} \dot{X} ^{\nu}$, and m is a constant related to the mass of the particle. This action is called the Nambu-Goto action. Consider a Lagrangian:
\begin{align}
    S_{\text{NG}} = -m\int_{\gamma} d\tau L(\tau)
\end{align}
The canonical momentum is:
\begin{align}
    p_{\mu} = \pdv{L}{\dot{X}^{\mu}} = \frac{m\dot{X}_{\mu}}{(-\dot{X}^{2})^1/2}
\end{align}
Then it ends up with a constraint:
\begin{align}
    p^{2} + m^{2} = 0
\end{align}
which illustrates that m is actually the mass of the particle. The equation of motion for $X^{\mu}$ gives:
\begin{align}
    m\ddot{X}^{\mu} =0
\end{align}
then we can see that the action is correctly describing the free propagation of the particle.
\subsubsection{The Polyakov Action}
We can suppose another action for a particle which is called the Polyakov action given:
\begin{align}
    S_{P} = \frac{1}{2} \int _{\gamma} d\tau e(\tau) \lbrace \frac{1}{e(\tau)^{2}} \dot{X}^{2} - m^{2} \rbrace
\end{align}
$e(\tau)$ is named the world-line metric. The equation of motion corresponding to this action is:
\begin{align}
    \dot{X}^{2} + m^{2} e(\tau) ^{2} =0
\end{align}
Using it, we can deform the Polyakov action by eliminating the world-line metric:
\begin{align}
    S_{P} = \frac{1}{2} \int _{\gamma} d\tau e(\tau) (-2m^{2}) = -m \int _{\gamma} d\tau(-\dot{X}^{2})^{1/2} = S_{\text{NG}}
\end{align}
Therefore, the Nambu-Goto action and the Polyakov action are equivalent to each other. The reason we use the polyakov action is that it is much easier to quantize.

\subsubsection{The String Worldsheet}
Let us do the same computations, but now we are dealing with a string, not a particle. Considering the motion of a string, it sweeps out a 2-dimensional worldsheet $\Sigma$ parametrized by two coordinates $(\sigma, \tau)$:
\begin{align}
    \Sigma : (\sigma,\tau) \hookrightarrow X^{\mu} (\sigma, \tau) \in \mathbb{R} ^{1,D-1}
\end{align}
Define the ranges:
\begin{align}
    0 \le \sigma \le 2\pi, & \qq{} \tau \in \mathbb{R}
\end{align}
SInce we are mostly interested in closed strings, rather than open ones, we impose the boundary condition given:
\begin{align}
    \sigma \simeq \sigma + 2\pi
\end{align}
So the string worldsheet parametrized by such coordinates forms a cylinder as shown in figure \ref{fig:worldsheet}.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=5pt]
        \draw[->] (0,0) -- (1,0) node[right=1pt]{$X^{i}$};
        \draw[->] (0,0) -- (0,1) node[left=2pt] {$X^{0}$};
        \node[cylinder, draw, shape aspect=.5, 
      cylinder uses custom fill, cylinder end fill=green!50, 
      minimum height=1cm,
      minimum width=0.5cm,
      cylinder body fill=green!25, opacity=0.5, 
    scale=3, rotate=90](c) at (.5,.5) {};
    \draw[->,red] (.5,.84) -- (.52,.84) node[above=1pt,black] {$\sigma$};
    \draw[->, red] (.65,.5) -- (.65,.5) node[right=1pt, black] {$\tau$};
    \draw[->, green] (.9,.8) node[right=2pt, black]{worldsheet $\Sigma$}-- (.7,.7); 
    \end{tikzpicture}
    \caption{The worldsheet of a string parametrized by two coordinates $(\sigma, \tau)$}
    \label{fig:worldsheet}
\end{figure}
It is useful to denote the coordinates as:
\begin{align}
    \lbrace \sigma, \tau \rbrace \equiv \xi ^{a}, & \qq{} a=0,1
\end{align}
With the worldsheet metric $h_{ab} (\xi)$, the string tension $T$ which can be written in terms of a parameter $\alpha '$:
\begin{align}
    T \equiv \frac{1}{2\pi \alpha '}    
\end{align}
the Polyakov actions for the string is given:
\begin{align}
    \label{eq:1.20}
    S_{P} = -\frac{T}{2} \int _{\Sigma} d^{2} \xi (-\text{det} h) ^{1/2} h^{ab} (\xi) \eta _{\mu \nu} \partial _{a} X^{\mu} (\xi) \partial _{b} X^{\nu} 
\end{align}
Besides, there are also the string length $l_{s}$ and the string scale $M_{s}$, given:
\begin{align}
    l_{s} \equiv \sqrt{\alpha '} , & \qq{} M_{s} \equiv \frac{1}{2\pi \sqrt{\alpha '}}
\end{align}
The worldsheet action eq.\ref{eq:1.20} should be viewed as a description of a two-dimensional theory with scalars $X^{\mu} (\xi)$, which is the sigma model. The space-time parametrized by $X^{\mu} (\xi)$ is known as the target space of the theory. The metric $\eta _{\mu \nu}$ on the space-time is the metric on the field space of the scalar fields $X^{\mu}$. Therefore, there are supposed to be different metrics on the field spaces for different target spaces in which strings propagate.

\subsubsection{Symmetries on the Worldsheet}
Eq \ref{eq:1.20} is invariant under:
\begin{align}
    \xi ^{a} \rightarrow \tilde{\xi} ^{a} (\xi)
\end{align}
In addition, it is invariant under the Weyl transformation given:
\begin{align}
    \delta X^{\mu} = 0, & \qq{} h_{ab} \rightarrow \tilde{h}_{ab} = e^{2\Lambda (\xi)} h_{ab}
\end{align}
The symmetries are useful for fixing the worldsheet metric $h_{ab}$. For D-dimensional theory, each number of degrees of freedom in the metric, a symmetric tensor, and so on. Particularly, the number of degrees of freedom in $h_{ab}$ is $\frac{1}{2}D(D+1)$, and for a string, $D=2$, the number of symmetry parameters is the same as the degrees of freedom in the metric. With symmetries, we can after all get:
\begin{align}
    h_{ab} = \eta _{ab} = 
    \begin{bmatrix}
        -1 & 0 \\
        0 & 1
    \end{bmatrix}
\end{align}
which is called flat gauge. Notice that it is still necessary to have equations of motion while the metric can be gauged. The equation of motion for the metric corresponding to the vanishing of the energy momentum tensor is:
\begin{align}
    T_{ab} =0
\end{align}
where:
\begin{align}
    T_{ab} \equiv \frac{4\pi}{\sqrt{-\text{det} h}} \fdv{S_{P}}{h^{ab}}
\end{align}
This condition is called a Virasoro constraint, and plays an important role for the quantization of the string. \\
\indent In flat gauge, the reduced Polyakov action is:
\begin{align}
    S_{P} = \frac{T}{2} \int _{\Sigma} d\sigma d\tau \lbrace (\partial _{\tau} X)^{2} - (\partial _{\sigma} X)^{2}  \rbrace
\end{align}
Now we can go to light-cone coordinates:
\begin{align}
    \xi ^{\pm} \equiv \tau \pm \sigma, & \qq{} \partial _{\pm} \equiv \frac{1}{2} (\partial _{\tau} \pm \partial _{\sigma})
\end{align}
Then the action deforms in those coordinates:
\begin{align}
    S_{P} = T\int _{\Sigma} d\xi ^{+} d\xi ^{-} \partial _{+} X \partial _{-} X
\end{align}
The equation of motion therefore for $X^{\mu}$ are:
\begin{align}
    \partial _{+} \partial _{-} X^{\mu} = 0
\end{align}
Thus $X^{\mu}$ can be thought of as the sum of left- and right-mooving parts of the strings as:
\begin{align}
    X^{\mu} = X_{L} ^{\mu} (\xi ^{+}) + X_{R} ^{\mu} (\xi ^{-})
\end{align}
Also considering the periodic boundary conditions $X^{\mu} (\tau, \sigma = 0) = X^{\mu} (\tau, \sigma = 2n\pi)$, the most general solution is:
\begin{align}
    \begin{split}
        & X_{R} ^{\mu} (\xi ^{-}) = \frac{1}{2} (x^{\mu}) +c^{\mu}) + \frac{1}{2}\alpha' p_{R} ^{\mu}\xi ^{-} + i\sqrt{\frac{\alpha'}{2}}\sum_{n\in\mathbb{Z}, n\neq 0} \frac{1}{n}\alpha_{n}^{\mu} e^{-in\xi^{-}} \\
        & X_{L} ^{\mu} (\xi ^{+}) = \frac{1}{2} (x^{\mu}) -c^{\mu}) + \frac{1}{2}\alpha' p_{L} ^{\mu}\xi ^{+} + i\sqrt{\frac{\alpha'}{2}}\sum_{n\in\mathbb{Z}, n\neq 0} \frac{1}{n}\tilde{\alpha}_{n}^{\mu} e^{-in\xi^{+}}
    \end{split}
\end{align}
where $x^{\mu}$, $c^{\mu}$, $p_{R}^{\mu}$, $p_{L}^{\mu}$, $\alpha _{n} ^{\mu}$, $\tilde{\alpha} _{n} ^{\mu}$ are constants. Due to the periodicity:
\begin{align}
    p_{R}^{\mu} = p_{L}^\mu \equiv p^{\mu}
\end{align}
Averaging over the string, one may find:
\begin{align}
    q^{\mu} \equiv \frac{1}{2\pi} \int _{0} ^{2\pi} d\sigma X^{\mu} = x^{\mu} + \alpha'p^{\mu} \tau
\end{align}
Thus we can say that $x^{\mu}$ is the center of mass position, and $p^{\mu}$ is the target space momentum. 

\subsubsection{Spectrum}
Considerations so far have been in classical manner, but it is needed to quantize strings in order to investigate the spectrum of excitations. In the following, we will manipulate so-called light-cone quantization. Introduce target-space light-cone coordinates:
\begin{align}
    X^{\pm} \equiv \frac{1}{\sqrt{2}} (X^{0} \pm X^{D-1}), & \qq{} X^{i}, & \qq{} i = 1,\dotso ,D-2
\end{align} 
Then the metric takes the form:
\begin{align}
     \eta _{+-} = \eta _{-+} = -1, & \qq{} \eta _{ij} = \delta _{ij}
\end{align}
With this, an inner product is defined:
\begin{align}
    X^{2} = -2X^{+}X^{-} + \dot {X}^{i} \dot {X}^{i}
\end{align}
The expansion of $X^{+}$ is:
\begin{align}
    X^{+} (\tau,\sigma) = x^{+} + \alpha' p^{+} \tau + i\sqrt{\frac{\alpha'}{2}} \sum _{n\in \mathbb{Z},n\neq 0} \frac{1}{n} \alpha _{n} ^{+} e^{-in\xi ^{-}} +i\sqrt{\frac{\alpha'}{2}} \sum _{n\in \mathbb{Z},n\neq 0} \frac{1}{n} \tilde{\alpha} _{n} ^{+} e^{-in\xi ^{+}}
\end{align}
Since there are residual symmetries even if we choose the light-cone gauge, we can set all the oscillator modes of $X^{+}$ to zero. Then:
\begin{align}
    X^{+} (\tau,\sigma) = x^{+} + \alpha'p^{+}\tau
\end{align}
Imposing the Virasoro constraints as well:
\begin{align}
    \partial _{\pm} X^{-} = \frac{1}{\alpha' p^{+}} (\partial _{\pm} X^{i})^{2}
\end{align}
We can observe that the $X^{-}$ oscillators are written in the transverse oscillators in $X^{i}$ too. Therefore, only the transverse oscillators are independent degrees of freedom. This is very useful because only $X^{i}$ contains physically independent oscillators and rules out tow unphysical polarizations of the string. The action in the light-cone gauge becomes:
\begin{align}
    S_{LC} &= \frac{1}{4\pi \alpha'} \int _{\sigma} d\tau d\sigma \lbrace (\partial _{\tau} X^{i})^{2} - (\partial _{\sigma} X^{i})^{2} + 2(\partial _{\sigma} X^{+} \partial _{\sigma} X^{-} - \partial _{\tau} X^{+} \partial _{\tau} X^{-}) \rbrace \nonumber \\
    &= \frac{1}{4\pi\alpha'} \int _{\sigma} d\tau d\sigma \lbrace (\partial _{\tau} X^{i})^{2} - (\partial _{\sigma} X^{i})^{2} - \int d\tau p^{+} \partial _{\tau} q^{-} \nonumber \\
    & \equiv \int d\tau L 
\end{align}
where defined as:
\begin{align}
    q^{-} \equiv \frac{1}{2\pi} \int _{0} ^{2\pi} d\sigma X^{-}
\end{align}
From this, canonical momenta are given:
\begin{align}
    p_{-} \equiv \pdv{L}{\dot{q}^{-}} = -p^{+}, & \qq{} \Pi _{i} \equiv \pdv{L}{\dot{X}^{i}}= \frac{\dot{X}_{i}}{2\pi \alpha'}
\end{align}
Then quantize the theory by introducing the canonical commutaion relations:
\begin{align}
    [X^{\mu}(\tau,\sigma), \Pi^{\mu} (\tau,\sigma;)] = i\eta ^{\mu \nu} \delta(\sigma - \sigma')
\end{align}
followed by:
\begin{align}
    [x^{i},p^i] &= i\delta_{ij}, \\
    [p^{+},q^{-}] &= i, \\
    [\alpha _{m}^{i},\alpha _{n}^{j}] &= m\delta_{m+n,0}\delta_{ij},\\
    [\tilde{\alpha}_{m}^{i}, \tilde{\alpha}_{n}^{j}] &= m\delta_{m+n,0} \delta_{ij} 
\end{align}
Then we can adopt the standard procedure of quantization by promoting the oscillator modes to operators acting on a Hilbert space as in QFT. In this case, $\alpha_{-n} ^{i}$ with $n>0$ are creation operators acting on a vacuum state $\ket{0,p}$. On the other hand $\alpha_{n}^{i}$ with $n>0$ represent annihilation operators. Recall that there are no oscillators to quantize for $X^{+}$, while the $X^{-}$ oscillators are given in terms of $X^{i}$. Explicitly:
\begin{align}
    \alpha _{n}^{-} = \frac{1}{2p^{+}\sqrt{2\alpha'}} \sum _{m=-\infty} ^{m=\infty} \alpha _{n-m} ^{i} \alpha _{m} ^{i}
\end{align}
Since the ordering of the $\alpha$ matters, we need the notions of normal ordered products and a normal ordering constant a where:
\begin{align}
    \alpha_{n} ^{-} = \frac{1}{2p^{+} \sqrt{2\alpha'}} \left( \sum_{m=-\infty} ^{m=\infty} :\alpha_{n-m}^{i} \alpha_{m}^{i}: -a\delta_{n,0} \right) 
\end{align}
with the definition:
\begin{align}
    :\alpha_{m}^{i} \alpha_{n}^{i}: \equiv 
    \begin{cases}
        \alpha_{m}^{i} \alpha_{n}^{i} & \quad \text{for } m \leq n \\
        \alpha_{n}^{i} \alpha_{m}^{i} & \quad \text{for } n < m 
    \end{cases}
\end{align}
\subsubsection{Lorentz Invariance}
So far we have performed quantization in special target-space light-cone coordinates. So we should also think about Lorentz invariance in the theory. Generally, the generators of the Lorentz transformations are given:
\begin{align}
    J^{\mu \nu} = \int _{0}^{2\pi} d\sigma (X^{\mu} \Pi ^{\nu} - X^{\nu} \Pi ^{\mu}) \equiv l^{\mu\nu} + E^{\mu\nu}+ \tilde{E}^{\mu\nu}
\end{align}
where
\begin{align}
    l ^{\mu\nu} &= x^{\mu} p^{\nu} - x^{\nu}p^{\mu} \\
    E^{\mu\nu} &= -i\sum_{n=1}^{\infty} \frac{1}{n} (\alpha_{-n}^{\mu}\alpha_{n}^{\nu} - \alpha_{-n}^{\nu} \alpha_{n}^{\mu}) \\
    \tilde{E^{\mu\nu}} &= -i\sum_{n=1}^{\infty} \frac{1}{n} (\tilde{\alpha}_{-n}^{\mu}\tilde{\alpha}_{n}^{\nu} - \tilde{\alpha}_{-n}^{\nu} \tilde{\alpha}_{n}^{\mu})
\end{align}
Lorentz algebra reads:
\begin{align}
    [J^{\mu\nu}, J^{\rho\sigma}] = i\eta ^{\mu\rho}J^{\nu\sigma} + i\eta^{\nu\sigma}J^{\mu\rho} - i\eta^{\mu\sigma}J^{\nu\rho} - i\eta^{\nu\rho}J^{\mu\sigma}
\end{align}
Particularly:
\begin{align}
    [J^{-i},J^{j}] = 0
\end{align}
but at the same time, this calculation followed by:
\begin{align}
    [J^{-i},J^{-j}] = -\frac{1}{(p^{+})^{2}} \sum_{m=1}^{\infty} \lbrace \frac{26-D}{12}m + \frac{1}{m}(\frac{D-26}{12} + 2(1-a))(\alpha_{-m}^{i} \alpha_{m}^{j} - \alpha_{-m}^{j} \alpha_{m}^{i}) + (\text{tilde terms}) 
\end{align}
So for the Lorentz invariance at quantum level, there are constraints such as:
\begin{align}
    D=26, & \qq{} a=1
\end{align}
It claims that the quantum bosonic string is only consistent in 26-dimensions. Such a restricion on the dimensionality is named criticality. Note that this is the case for the bosonic string, and for the superstring, the number of dimensions is 10.

\subsubsection{Quantum String Spectrum}
Let us study the spectrum of the quantized string. The Hamiltonian is:
\begin{align}
    \begin{split}
    H &= p_{-} \dot{q}^{-} +\int _{0}^{2\pi} d\sigma \Pi _{i} \dot{X}^{i} - L \\
    &=\frac{1}{4\pi\alpha'} \int_{0}^{2\pi}d\sigma  \left[ (\partial_{\tau} X^{i})^{2} + (\partial _{\sigma} X^{i})\right] \\
    &= \frac{\alpha'}{2}p^{i}p^{i} + \frac{1}{2} \sum_{n=-\infty}^{\infty} (\alpha_{-n}^{i} \alpha_{n}^{i} + \tilde{\alpha}_{-n} ^{i} \tilde{\alpha} _{n}^{i})
    \end{split}
\end{align}
From the Virasoro constraint:
\begin{align}
    \partial _{\tau} X^{-} = \frac{1}{2p^{+}\alpha'} \left[ (\partial_{\tau}X^{i})^{2} + (\partial _{\sigma} X^{i})^{2}\right]
\end{align}
we may have:
\begin{align}
    p^{-} = \frac{1}{2\pi\alpha'}\int_{0}^{2\pi} d\sigma \partial _{\tau} X^{-} = \frac{H}{\alpha' p^{+}}
\end{align}
Considering normal ordering of $\alpha$:
\begin{align}
    p^{+}p^{-} = \frac{1}{\alpha'} \left[ \sum_{n=1} ^{\infty} :\alpha _{-n}^{i} \alpha_{n}^{i}: + \sum_{n=1}^{\infty} :\tilde{\alpha}_{-n}^{i} \tilde{\alpha} _{n}^{i}: -2a + \frac{\alpha'}{2}p^{i}p^{i} \right]
\end{align}
The mass in the target space is:
\begin{align}
    M^{2} = -p^{2} = 2p^{+}p^{-} -p^{i}p^{i} = \frac{2}{\alpha'} \left[ \sum_{n=1} ^{\infty} :\alpha _{-n}^{i} \alpha_{n}^{i}: + \sum_{n=1}^{\infty} :\tilde{\alpha}_{-n}^{i} \tilde{\alpha} _{n}^{i}: -2a \right]
\end{align}
But for the closed string there is a symmetry regarding translations along $\sigma$ implying the level matchong condition:
\begin{align}
    \sum_{n=1} ^{\infty} :\alpha _{-n}^{i} \alpha_{n}^{i}: = \sum_{n=1}^{\infty} :\tilde{\alpha}_{-n}^{i} \tilde{\alpha} _{n}^{i}:
\end{align}
this leads to the mass expression in:
\begin{align}
    M^{2} = \frac{4}{\alpha'} (\sum_{n=1} ^{\infty} :\alpha _{-n}^{i} \alpha_{n}^{i}: -1)
\end{align}
applying the criticality to fix $a=1$. Now we can start to study the spectrum. Let us define $\sum_{n=1} ^{\infty} :\alpha _{-n}^{i} \alpha_{n}^{i}: = N$. \\
For $N=0$ case, we have:
\begin{align}
    M^{2}= -\frac{4}{\alpha'}
\end{align}
This is a tachyonic mode and suggesting an instability in the bosonic string. \\
For $N= 1$:
\begin{align}
    M^{2}=0
\end{align}
So it is the massless spectrim, and given by:
\begin{align}
    \xi _{ij} \tilde{\alpha}_{-1}^{i} \alpha_{-1}^{j} \ket{0,p}, & \qq{} i,j=1.\dotso ,24
\end{align} 
The tensor $\xi_{ij}$ can be decomposed into irreducible representations of SO(24):
\begin{align}
    \xi _{ij} = g_{(ij)} + B_{[ij]} + \Phi
\end{align}
where $g_{(ij)}$ and $B_{[ij]}$ are traceless symmetric and anti-symmetric respectively as well as $\Phi$ represents a scalar. Thus we obtain a massless, transversely polarized symmetric tensor fields $g_{ij}$, which is a graviton. Therefore the quantum string contains gravitational modes in spectrum. \\
For $N>1$, we may have massive oscillator string modes.

\subsection{Realization of the Distance Conjecture}
We have found that the bosonic string lives in 26-dimensions, and mentioned the superstring does in 10-dimension. Those facts seem to make them incompatible directly with the observed universe. Nevertheless, they can be observed yet since the additional dimensions might be compact and small. In this language, it is naturall to think about string theory in a spacetime which has a compact direction. One of possible settings is the case where one of the dimensions is in the form of a circle. Studying this, we will see a realization of the Distance conjecture.

\subsubsection{Compactification on a Circle}
Consider $D=d+1$ dimensional spacetime. Let the spatial direction $X^{d}$ be compact in the shape of a circle with periodicity:
\begin{align}
    X^{d} \simeq X^{d} +1
\end{align}
notice that we are working in Planck units, so the periodicity is set to one in those units. \\
\indent The metric on the D-dimensional space is given:
\begin{align}
    \label{eq:met}
    ds^{2} \equiv G_{MN} dX^{M}dX^{N} = e^{2\alpha\phi}g_{\mu\nu} dX^{\mu}dX^{\nu} + e^{\beta\phi}(dX^{d})^{2}
\end{align}
There some coordinates and parameters are introduced. Coordinates $X^{M}$ are D-dimensional, $M=0, \dotso , d$, while $\mu = 0, \dotso ,d-1$. The D-dimensional metric is $G_{MN}$, and d-dimensional one is $g_{\mu\nu}$. The metric has a parameter $\phi$ which represents a d-dimensional scalar field. In addition, the constants $\alpha$ and $\beta$ have been defined:
\begin{align}
    \alpha^{2} = \frac{1}{2(d-1)(d-2)} , & \qq{} \beta = -(d-2) \alpha
\end{align}
The circumference of the circle denoted $2\pi R$ is:
\begin{align}
    \label{eq:circ}
    2\pi R \equiv \int _{0}^{1} \sqrt{G_{dd}}dX^{d} = e^{\beta\phi}
\end{align}
Then the radius is a dynamical field in d-dimensions. Our interest will be in the behaviors of the d-dimensional theory under variations of the expectation value of the field $\phi$, which amounts to variations of the size of the circle. \\
\indent Consider the decomposition of the D-dimensional Ricci scalar $R^{D}$ for the metric \ref{eq:met}. We have:
\begin{align}
    \label{eq:eff}
    \int d^{D}X \sqrt{-G} R^{D} = \int d^{d}X \sqrt{-g} \left[R^{d} -\frac{1}{2} (\partial \phi)^{2} \right]
\end{align}
Introduce a massless D-dimensional scalar field $\Psi$. Due to the periodicity:
\begin{align}
    \Psi (X^{M}) = \sum_{n=-\infty}^{\infty} \psi_{n} (X^{\mu}) e^{2\pi i n X^{d}}
\end{align}
The modes $\psi _n$ are d-dimensional scalar fields caleld Kaluza-Klein (KK) modes, and $\psi _{0}$ is the zero-mode of $\Psi$. The momentum is quantized along the compact direction:
\begin{align}
    -i\pdv{X^{d}} \Psi = 2\pi n \Psi
\end{align}
Now to make things simple, assume $g_{\mu\nu} = \eta _{\mu\nu}$. The equation of motion for $\Psi$ is:
\begin{align}
    \partial ^{M} \partial _{M} \Psi = (e^{-2\alpha \phi} \partial ^{\mu} \partial _{\mu} + e^{-2\beta \phi} \partial _{X^{d}}^{2}) \Psi = 0
\end{align}
since $\Psi$ is massless. Then this leads the equation of motion for $\psi _n$ modes:
\begin{align}
    \left[\partial ^{\mu}\partial _{\mu}- (\frac{1}{2\pi R})^{2} (\frac{1}{2 \pi R})^{\frac{2}{d-2}} (2\pi n)^{2}  \right] \psi _{n} = 0
\end{align}
Therefore, the mass of the KK modes can be read off as:
\begin{align}
    M_{n} ^{2}= (\frac{n}{R})^{2} (\frac{1}{2 \pi R})^{\frac{2}{d-2}}
\end{align}
Thus, in the $d$-dimensional theorym the KK modes are a massive tower of states whose masses increases.

\subsubsection{Compactification of String on a Circle}
Now let us do the same procedure in the string theory considering strings on a circle of radius R. A metric is given:
\begin{align}
    \label{eq:metric}
    ds^{2} = \eta _{MN} dX^{M} dX^{N}
\end{align}
taking the $X^{d}$ direction as R-periodic:
\begin{align}
    X^{s} \simeq X^{d} + 2\pi R
\end{align}
Consider the bosonic mode expansion as before but for now, we will not impose $X^{M} (\sigma + 2\pi, \tau) = X^{M} (\sigma,\tau)$. Thus:
\begin{align}
    X^{M} (\tau, \sigma) = x^{\mu} + \alpha' p^{M} \tau + \frac{\alpha'}{2}(p_{L}^{M} - p_{R}^{M}) \sigma + \text{oscillator}
\end{align}
Here left- and right mooving momenta are considered independently, and the overall momentum is:
\begin{align}
    \frac{1}{2} (p_{R}^{M} + p_{L} ^{M})
\end{align}
In the non-compact space, imposing $X^{\mu} (\sigma+2\pi, \tau) = X^{\mu}(\sigma,\tau)$, we have $p_{R}^{\mu} = p_{L}^{\mu}$. However, for a circle we have a winding:
\begin{align}
    X^{d} (\sigma +2\pi, \tau) = X^{d} (\sigma,\tau) + w 2\pi R ,& \qq{} w \in \mathbb{Z}
\end{align}
The string is wrapping around a circle w times. Therefore, we may have:
\begin{align}
    \frac{\alpha'}{2} (p_{L}^{d} - p_{R}^{d}) =wR
\end{align}
Consider the mass spectrum for the string by going to target space light-cone gauge again. The hamiltonian reads:
\begin{align}
    H = \frac{\alpha'}{2} \left[ \frac{1}{4} (p_{L}^{d} -p_{R}^{d})^{2} +p^{\alpha} p^{\alpha} + (p^{d})^{2} \right] + (N + \tilde{N} -2)
\end{align}
here we split the index $i = \lbrace \alpha, d \rbrace$. Notice in this case we no longer have the level matching condition, but instead:
\begin{align}
    N-\tilde{N} = nw
\end{align} 
Then the d-dimensional mass is given by $-p_{\mu} p^{\mu} = 2p^{+} p^{-} - p^{\alpha} p^{\alpha}$ which leads:
\begin{align}
    \label{eq:1.90}
    (M_{n,w})^{2} = (\frac{n}{R})^{2} + (\frac{wR}{\alpha'})^{2}
\end{align}
We want to make it related to the effectiv eaction \ref{eq:eff}. Nevertheless, we need to change form the metric \ref{eq:metric} to the one \ref{eq:met}. This procedure is called going from the string frame to the Einstein frame. The difference is the factor of $e^{2\alpha\phi}$ multiplying the $g_{\mu\nu}$ directions. An important object is the d-dimensional scalar $\Psi$, called dilaton, defined as:
\begin{align}
    \Psi^{d} \equiv \Psi - \frac{1}{2} \log (2\pi R M)
\end{align}
We would like to observe variations of R which maintain $\Psi ^{d}$ fixed. That is, we must vary:
\begin{align}
    e^{2\Psi} \sim \frac{1}{2\pi R M}
\end{align}
But considering the definition of the d-dimensional Planck mass $M_{p}^{d}$:
\begin{align}
    \frac{(M_{p}^{d})^{d-2}}{2} \equiv 2\pi M^{D-2} e^{-2\Psi}
\end{align}
From this we can see that in order to remain the Einstein frame $M_{p} ^{d} = 1$, we must choose our units so that:
\begin{align}
    M \sim (2\pi R) ^{\frac{1}{d-2}}
\end{align}
This affects the mass of the winding modes in \ref{eq:1.90}. \\
\indent Finally, performing the change of frames leads to the Einstein frame mass gives:
\begin{align}
    \label{eq:efram}
    (M_{n,w})^{2} = (\frac{1}{2\pi R})^{\frac{2}{d-2}} (\frac{n}{R})^{2} + (2\pi R)^{\frac{2}{d-2}} (\frac{wR}{\alpha_{0}'})^{2}
\end{align}

\subsubsection{Distance Conjecture}
We will now study the d-dimensional effective theory. The action is given in \ref{eq:eff} and this has to be supplemented by the spectrum \ref{eq:efram}. Our particular interest is how the spectrum of states behaves under variations of the expectation value of the field $\phi$. This can be determined easily from the relation \ref{eq:circ}. The possible expectation values of the field $\phi$ define a field space $\mathcal{M}_{\phi}$, which has now one infinite real dimension. Thus consider:
\begin{align}
    \mathcal{M}_{\phi} : -\infty < \phi < \infty
\end{align}
We are now having two infinite towers of massive states in this theory, in eq \ref{eq:efram}, the tower of KK modes with masses $M_{n,0}$, and of winding modes with $M_{0,m}$. Using the relation \ref{eq:circ}, those mass scales can be written as:
\begin{align}
    M_{\text{KK}} \sim e^{\alpha\phi}, & \qq{} M_{w} \sim e^{-\alpha \phi}
\end{align}
where
\begin{align}
    \alpha = \sqrt{2} (\frac{d-1}{d-2})^{1/2} > 0
\end{align}
For any variation $\Delta \phi$ there exists an infinite tower of states with associated mass scale M. We can also see that such a tower becomes light at an exponential rate in $\Delta \phi$:
\begin{align}
    \label{eq:mass}
    M(\phi_{i} + \Delta \phi) \sim M(\phi _{i})e^{-\alpha \abs{\Delta \phi}}
\end{align}
as illustrated in figure \ref{fig:dual}.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=5]
        \draw[->] (-0.7,0) node[below=2pt] {$-\infty$} -- (0.7,0) node[below=2pt] {$+\infty$};
        \draw[->] (0,-.5) -- (0,0.5) node[left=2pt] {$\ln \frac{M}{M_{p}}$};
        \draw[blue] (-0.6,-0.4) -- (0.6,0.4) node[above=2pt,black] {$M_{KK}$};
        \draw[red] (-.6,0.4) node[above=2pt, black] {$M_{w}$} -- (0.6,-0.4);
        \draw (0.7,0) node[above=2pt] {$\phi$};
    \end{tikzpicture}
    \caption{Illustration of the mass scales on a log plot. For the KK and winding towers as a function of the scalar field $\phi$ expectation value.}
    \label{fig:dual}
\end{figure}
There are a few things to note:
\begin{itemize}
    \item {The tower of states becoming light is the KK tower if $\Delta \phi <0$ while it is the winding tower when $\Delta \phi >0$. That is, either tower of states always becomes light regardless of the sign of $\Delta\phi$ is.}
    \item {This is a characteristic feature of the string theory. It is not true in QFT since winding states are absent in field theories.}
    \item {The product of the mass scales of the two towers is independent of $\phi$.}
    \item {The exponent $\alpha$ is a constant of order one $\order{1}$.}
    \item {When $\abs{\Delta \phi} \rightarrow  \infty$, an infinite number of states get massless.} 
\end{itemize}
The last point has a discussion. If we consider an effective field theory which has a cut-off $\Lambda$ below the mass scale of an infinite tower of states, then this teory can be valid only for a finite range of expectation values of $\phi$. \\
\indent The exponential behavior is particularly interesting. Those towers are deeply related to each other as there is a $\mathbb{Z}_{2}$ symmetry which interchanges them. This relation is called T-duality, and it is able to be seen directly in the string frame where the mass spectrum is invariant under the action. 
\begin{align}
    \text{T-duality} : R \Leftrightarrow \frac{\sqrt{\alpha'}}{R}
\end{align}
Actually, it is a symmetry not only for the mass, but also for the full string theory. There are many other kinds of dualities other than T-duality. Then it is natural to think that there are many different towers of states which are dual so that as one moves in a space of the theory, the product of the mass scale of the dual towers remains constant and thus one must become light in any direction. Then as we move an infinite distance in a parameter space, the tower must be getting light. \\
\indent Those discussions and examples let to the proposal of the Swampland Distance Conjecture, which is similar to \ref{eq:mass}, but more generally stated in the next section.



\subsection{Swampland Distance Conjecture}
Consider an EFT coupled to Einstein gravity with moduli space $\mathcal{M}$ parametrized by scalar fields, and whose metric $g_{ij}$ is given by its kintic term. The first statement of the conjecture is as follows: Starting from a point $P \in \mathcal{M}$, there always exits a point $Q \in \mathcal{M}$ at infinite geodesic distance $d(P,Q)$. The second part of the conjecture describes a phenomena supposed to happen as approaching a point at infinite field distance limits:
\begin{tcolorbox}[title=Swampland Distance Conjecture,
    title filled=false,
    colback=blue!5!white,
    colframe=blue!75!black]
    There happens an infinite tower of states that becomes exponentially light with the geodesic distance such as 
    \begin{align}
        M(Q) \sim M(P) e^{-\lambda d(P,Q)}
    \end{align}
    with $\lambda$ an $\order*{1}$ constant in Planck units \parencite{ooguri_geometry_2007}. 
\end{tcolorbox}
The exponential decay rate $\lambda$ is not specified by the conjecture except that it should be positive. However it is predicted to be an $\order{1}$ constan as otherwise it could wreck the exponential behavior, while where it derived from is still unknown. One of the open question around this conjecture is in fact to determine how small $\lambda$ can be. Some significant progress on seeking of the concrete lower bounds have been achieved in the string theory frameworks as proposed in \parencite{gendler_merging_2021, bedroya_trans-planckian_2020, andriot_web_2020, lanza_swampland_2021}.
The behavior of SDC is schematically illustrated in figure \ref{fig:moduli}.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=3]
        \draw[outer color=red,inner color=white] (10:1) arc (10:30:1) -- (1.414,1.414) -- (60:1) arc (60:120:1) -- (-1.414, 1.414) -- (150:1) arc (150:170:1) -- (-2,0) -- (190:1) arc (190:210:1) -- (-1.414,-1.414) -- (240:1) arc (240:300:1) -- (1.414,-1.414) -- (330:1) arc (330:350:1) -- (2,0) -- (10:1);
        \draw (2,0) node[right=2pt] {$Q_{2}$};
        \draw (1.414,1.414) node [right=2pt] {$Q_{1}$};
        \draw (-1.414,1.414) node[left=2pt] {$Q_{3}'$};
        \draw(-2,0) node[left=2pt] {$Q_{2}'$};
        \draw(-1.414,-1.414) node[left=2pt] {$Q_{1}'$};
        \draw(1.414,-1.414) node[left=2pt] {$Q_{3}$};
        \draw[<->] (0,0) node[right =2pt] {$P$} -- (1.414,1.414); 
        \draw (30:1.4) node[right=2pt] {$d(P,Q_{1}) \rightarrow \infty $};
    \end{tikzpicture}
    \caption{Showing the behavior of SDC on a moduli space. From an arbitrary point $P$ in the bulk of moduli space, there are points $Q_i$ and $Q_{i}'$ which are infinitely far from $P$. The mass scale of the tower of states in a theory decays to zero as being close to any point $Q_{i}$, and it is shown by color. Note that due to T-duality as mentioned above, points at infinity $Q_{i}$ and $Q_{i}'$ are related, and the light towwer of states are interchanged between them.}
    \label{fig:moduli}
\end{figure}
Since an EFT cannot deal with infinitely many degrees of freedom under its cut-off, the emergence of the infinite tower of states indicates the breakdown of EFT. Thus, there is supposed to be a quantum gravity cut-off associated to the infinite tower of states, which decreases exponentially with the geodesic distance:
\begin{align}
    \label{eq:qg}
    \Lambda  _{\text{QG}} = \Lambda_{0} e^{-\lambda d(P,Q)}
\end{align}
as shown in fig.\ref{fig:cut}.
\begin{figure}[h]
    \centering
    \begin{tikzpicture}[scale=4]
        \draw[->] (-0.1,0) -- (2,0) node[right=2pt] {$d(P,Q)$};
        \draw[->] (0,-0.1) -- (0,1.2) node[above=2pt] {$\Lambda_{\text{QG}}$};
        \draw[samples=400,domain=0.01:1.9,smooth,variable=\x,blue] plot ({\x}, {exp((-3*\x))});
    \end{tikzpicture}
    \caption{Quantum gravity cut-off decays exponentially as we approach an infinite distance limits, because of the light tower of states expected from SDC.}
    \label{fig:cut}
\end{figure}
Note that since this is an asymmptotic statement about infinite distance $d(R_{i}, R_{f}) \to \infty$, the mass scale value at $R_{i}$ is not that important. From the perspective of QFT, this is really surprising. As it has been seen, the conjecture can holds only due to the string theory, more generally, quantum gravity. The typical mass scale for such physics is $M_{p}$. However, this conjecture claims that if in the bulk of moduli space, the tower of states has a mass scale around the Planck mass, and then at large expectation values, this is getting lower than $M_{p}$. Thus, it states that the naive application of decoupling on effective QFT breaks down at an exponentially lower energy scale than expected whenever a field develops a large expectation value.\\
\indent One important consequence is that EFTs are only valid for finite field variations. Since we are dealing with $\Lambda _{0} \leq M_{p}$ and considering eq.\ref{eq:qg}:
\begin{align}
    \Lambda = \Lambda_{0} e^{-\lambda d(P,Q)} \leq M_{p} e^{\lambda d(P,Q)}
\end{align}
then we may find:
\begin{align}
    d(P,Q) \leq \frac{1}{\lambda} \ln \frac{M_{p}}{\Lambda}
\end{align}
This claims that the maximum field variation depends on the cut-off scale of an EFT. It suggests that the higher cut-off is, the smaller the maximum field distance which can be described within the EFT is. \\
\indent On the other hand, we have an simple example of a moduli space which violates SDC. Suppose a periodic scalar $\phi \sim \phi + 2\pi$, which defines a circle $\mathcal{M} = S^{1}$. It violates SDC because the maxumum distance between two points on such a moduli space is $2\pi$. It does not mean that the periodic scalars are forbidden with quantum gravity, but they just must be included within a larger moduli space. \\
\indent To sum up, the SDC can be thought of as a constraint on the validity for finite field variations, as an EFT at a point in moduli space cannot be extended to an arbitrary far point from initial one. By approaching such a point, an infinite number of degrees of freedom would become exponentially light and eventually an EFT description broken. So far computations for the distance have been considered on the moduli space. Nevertheless, this notion of the distance can be generalized to the one between more generic field with a generic metric given also by the kinetic term \parencite{lust_ads_2019}. It will be investigated how the renormalization group affects on the statement of this conjecture later. \\
\indent As discussed previously, the realiztion of SDC is closely related to the property of T-duality. When a radius is sent to zero, the winding modes are replaced with a KK tower becoming light. In string theory, it is commonly accepted that a dual description arises in such symptotic limits. Therefore, SDC can be said a Duality conjecture as it is predicting the existence of a duality at every infinite distance limit. In this language, we can say that trying to understand SDC is linked to study the reasons why dualities exist. That connection motivates us to propose a refinement of SDC, which is called the Emergent String Conjecture \parencite{lee_emergent_2022}. 

\section{Weak Gravity Conjecture}
So far, we have enough information about the Swampland for our computations. However, since SDC also has a strong connection with Weak Gravity Conjecture \parencite{arkani-hamed_string_2007}, we will provide some information about it in this section and its connection with SDC. The Weak Gravity Conjecture is stated as follows:
\begin{tcolorbox}[title=Weak Gravity Conjecture,
    title filled=false,
    colback=blue!5!white,
    colframe=blue!75!black]
    Consider a theory coupled to gravity with a U(1) gauge symmetry with gauge coupling e, then
    \begin{itemize}
        \item {\textbf{Electric Weak Gravity Conjecture}: There exists in the theory with mass m and charge q such that
        \begin{align}
            \label{eq:ewgc}
            m^{2} \leq 2e^{2} q^{2} M_{p}^{2}
        \end{align}
        }
        \item {\textbf{Magnetic Weak Gravity Conjecture}: The cut-off scale $\Lambda$ of the theory is bounded from above
        \begin{align}
            \label{eq:mwgc}
            \Lambda \lesssim eM_{p}
        \end{align}}
    \end{itemize}
\end{tcolorbox}
The black hole arguments for the conjecture is in some sense similar to the ones for the absence of global symmetries in quantum gravity. Consider the Einsten-maxwell theory, and its black hole solutions, which are characterized by mass M, and quantized charge Q. Such charged black holes must satisfy the extremality bound given:
\begin{align}
    M^{2} \geq 2e^{2} QM_{p}^{2}
\end{align}
If this inequality is not achieved, it implies that the absence of horizons and the presence of naked singularity, which is considered to be problematic according to cosmic censorship \parencite{penrose_golden_2002}. Considering the Hawking radiation, the black holes which satisfy the bound evaporate loosing their mass and charge until they saturate the inequality. So assuming Q is large enough, there will be black holes with mass $M \sim eQM_{p}$. If those black holes are stable, in weak coupling limit, there are supposed to be an arbitrary number of black holes for a finite mass range. This is the situation we had when we were talking about the absence of global symmetries. In order to avoid existence of those remnants, it is required that the extremal black holes may decay. One of decay products would has a charge smaller than its mass or sturates the extremality bound. Then the charge of the other product cannot be smaller than its mass. The second product violates the cosmic censorship. Therefore, in order for the decay to occur, it cannot be a black hole, but a particle. This is the motivation for the Weak Gravity Conjecture. Once we see the electric version, the magnetic version can be also deduced by considering a monopole. The magnetic charge is proportional to the magnetic gauge coupling, which is inverse of the electric one. So we have a relation:
\begin{align}
    m \leq \frac{M_{p}}{e}
\end{align}
But the mass of monopole is also at least at the order of the cut-off scale of the theory over gauge coupling squared:
\begin{align}
    m \sim \frac{\Lambda}{e^{2}}
\end{align}
This suggests that the cut-off scale is bounded as follows:
\begin{align}
    \Lambda \le eM_{p}
\end{align}
There are a lot of attempts towards the Weak Gravity Conjecture from various aspects such as black holes, AdS/CFT, and string theory \parencite{montero_weak_2016,hod_proof_2017,crisford_testing_2018, cheung_proof_2018, hamada_weak_2019,andriolo_tower_2018-1}. Also the conjecture has been sharpen for certain cases. \\
\indent Notice that the behavior of deacying cut-off scale $\Lambda$ as the coupling is sent to zero in SDC is predicted by the magnetic Weak Gravity Conjecture.